Introducing statistics with \\texttt{intRo}

### 2014-12-04 student-paper-competition-2014/paper.Rmd
Blurb on store buttons

\texttt{intRo} leverages reactive programming techniques as data is manipulated by the user, this carries throughout the entire session. In a typical \texttt{shiny} app, users interact with inputs, which in turn yield different results. Within \texttt{intRo}, the users are able to interact and manipulate the data underlying the entire application. This posed many challenges in the creation of \texttt{intRo}, namely timely save points according to the user's timeline, and reactive updating of variable lists tied to inputs across the entire application.

\ak{[Add information about save buttons for individual pieces of code]}

>>>>

\texttt{intRo} leverages reactive programming techniques as data is manipulated by the user, this carries throughout the entire session. In a typical \texttt{shiny} app, users interact with inputs, which in turn yield different results. Within \texttt{intRo}, the users are able to interact and manipulate the data underlying the entire application. This posed many challenges in the creation of \texttt{intRo}, namely timely save points according to the user's timeline, and reactive updating of variable lists tied to inputs across the entire application. Because the user may experiment with different configurations or select different variables, we did not want to store all actions taken in the intRo session. Rather, each module includes a button allowing the user to explicitly store the output visible in the results panel into the R script. This way, output is only stored when the user is satisfied, and the resulting output is not cluttered with unnecessary information.
